Playing against Nature: causal discovery for decision making under uncertainty

### 2018-05-16 Segundo_Semestre/CausalML_Workshop/Paper_long_version.tex
cambios intro

\icmlcorrespondingauthor{Cieua Vvvvv}{c.vvvvv@googol.com}
\icmlcorrespondingauthor{Eee Pppp}{ep@eden.co.uk}

@@

\section{Introduction}
A fundamental part of intelligent reasoning  is being able to make decisions under uncertain conditions (\cite{lake2017building}, \cite{danks2014unifying}). In some cases, a decision maker who faces an uncertain environment has enough information to make choices by maximizing expected utilities. If enough information is not available, the decision maker could try to \textit{learn} from the environment by interacting with it.

Learning by interaction has been extensively studied in Reinforcement Learning \cite{sutton1998reinforcement}, but the most common used techniques are purely reactive (\cite{garnelo2016towards}) and do not consider any structure of the environment beyond what is expressable in an MDP.

Since human beings are known to learn causal graphical models in sequential decision making processes (\cite{sloman2006causal}, \cite{nichols2007decision}, \cite{meder2010observing}, \cite{hagmayer2013repeated}, \cite{danks2014unifying}), although this learning is not perfect (\cite{rottman2014reasoning}).

In this paper which we propose that an autonomous agent can learn and use causal information while interacting with an uncertain environment which is governed by a fixed \textit{causal mechanism} unknown to the agent.

>>>>

@@

\section{Introduction}
A fundamental part of intelligent reasoning  is being able to make decisions under uncertain conditions (\cite{lake2017building}, \cite{danks2014unifying}). In some cases, a decision maker who faces an uncertain environment has enough information to make choices by maximizing expected utility, which is the formal criteria for making decisions if rational preferences are assumed (\cite{bernardo2000bayesian}, \cite{gilboa2009decision}). On the other hand, if enough information is not available, the decision maker could try to \textit{learn} from the environment by interacting with it.

Learning by interaction has been extensively studied by computer scientists using the Reinforcement Learning  setting \cite{sutton1998reinforcement}, but the most common used techniques  in this field are purely reactive and do not consider any high-level structure of the environment beyond what is expressable in a Markov Decision Process (\cite{garnelo2016towards}).

Since human beings are known to learn causal graphical models in sequential decision making processes (\cite{sloman2006causal}, \cite{nichols2007decision}, \cite{meder2010observing}, \cite{hagmayer2013repeated}, \cite{danks2014unifying}), although this learning is not perfect (\cite{rottman2014reasoning}) ,we propose that an autonomous agent can learn and use causal information while interacting with an uncertain environment which is governed by a fixed \textit{causal mechanism} unknown to the agent.
